Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-07 volunteer-clouds-ieee-ci-si.tex
More work on workers

Javascript has commonly been used to develop client-side scripts that handle the interaction 
with the user, communicate asynchronously with servers and update the content that is displayed \cite{flanagan2006javascript}.
Long-running scripts like those proposed in this work can interfere with the responsiveness of 
the page. The Web Workers specification \cite{hickson2012web} defines an API that allows Web developers 
to execute scripts in parallel with user interaction scripts of the main page. 
Worker scripts are spawned in the background allowing a thread-like operation with 
message-passing as the coordination mechanism.

>>>>

Javascript has commonly been used to develop client-side scripts that handle the user interface,
communicate asynchronously with servers and update the content that is displayed \cite{flanagan2006javascript}.
Long-running scripts like those proposed in this work can interfere with the responsiveness of 
the web application, because everything is handled by a single thread. 
The Web Workers specification \cite{hickson2012web} defines an API that allows Web developers 
to execute long-running scripts in parallel with the scripts of the main page. 
Worker scripts are spawned in the background allowing a thread-like operation using 
message-passing as the communication mechanism between the worker's execution environment and the main thread. 
According to the Web Workers W3C Candidate Recomendation \cite{hickson2012web} 
workers are expected to be long-lived, they have a high start-up performance cost, 
and a high per-instance memory cost. The Web Worker API is implemented in current
versions of both desktop and mobile web browsers. For volunteer computing using the Web Worker API   
brings several advantages over a single threaded implementation:
\begin{itemize}
\item If the browser uses a tabbed document interface, the worker script 
keeps running in the background even it the user brings forward another tabbed window.
\item Several instances of the NodEO script can be executed in parallel in a single web page. 
\item Many immplemantations of the Web Worker API can use multiple CPUs for the execution
of worker scripts, in particular the execution in multiple CPUs was tested in desktop verions of
Chrome, FireFox and Safari.

\end{itemize}
